Designing Turk Experiments for Visual Statistical Inference

### 2013-06-14 paper_turk.tex
some typos

There have been some advancements in visual statistical inference since it was first introduced by Buja \cite{buja:2009} where they have proposed formal methods for testing the significance of findings using lineup protocols. In visual statistical inference the test statistics is a plot of the observed data. This plot is placed randomly in a layout of plots called lineup. The rest of the plots in the lineups are generated from the model specified by the null hypothesis. A human observer is asked to evaluate the lineup. If the observer detects the actual plot in the lineup, the null hypothesis is rejected.

@@

The power of visual test is studied by \cite{majumder:2013} and it is revealed that power could be as good as conventional test and in some scenerios even better. But where the conventional test does not exists, visual inference could be the only inferential procedure without compromising a lot in power.

@@

\subsection{Selecting Parameter to Simulate Lineup} The first consideration for a simulation experiment is to fix the parameters of the model of interest. The very first consideration is the sample size. Other parameters depends on the model of interest. For example we have fixed the parameters in our first Amazon Mechanical Turk experiment as shown in table \ref{tbl:experiment_params}.

\subsection{Procedure to Simulate Data Plot} \label{sec:simulate_plot} In the simulation study the very first step is to generate a random sample of data from model of interest for prespecified parameters. We call this data set observed data. While the effect of the natural variability of this data set could be contolled by taking the replication of few samples, it is desirable to study whether we can reduce this variability alternatively. The main reason is to minimize the cost. To make sure that the observed data set truly represents model of interest we are considering three approaches. One is Kolomogorov test statistic approach and the other two approaches are quantiles of p values and closeness of estimated parameters to the true parameters. These three approaches are discussed below.\\

>>>>

There have been some advancements in visual statistical inference since it was first introduced by \cite{buja:2009} where they have proposed formal methods for testing the significance of findings using lineup protocols. In visual statistical inference the test statistics is a plot of the observed data. This plot is placed randomly in a layout of plots called lineup. The rest of the plots in the lineups are generated from the model specified by the null hypothesis. A human observer is asked to evaluate the lineup. If the observer detects the actual plot in the lineup, the null hypothesis is rejected.

@@

The power of visual test is studied by \cite{majumder:2013} and it is revealed that power could be as good as conventional test and in some scenarios even better. But where the conventional test does not exists, visual inference could be the only inferential procedure without compromising a lot in power.

@@

\subsection{Selecting Parameter to Simulate Lineup} The first consideration for a simulation experiment is to fix the parameters of the model of interest.

%The very first consideration is the sample size. Other parameters depends on the model of interest. For example we have fixed the parameters in our first Amazon Mechanical Turk experiment as shown in table \ref{tbl:experiment_params}.

\subsection{Procedure to Simulate Data Plot} \label{sec:simulate_plot} In the simulation study the very first step is to generate a random sample of data from model of interest for pre-specified parameters. We call this data set observed data. While the effect of the natural variability of this data set could be controlled by taking the replication of few samples, it is desirable to study whether we can reduce this variability alternatively. The main reason is to minimize the cost. To make sure that the observed data set truly represents model of interest we are considering three approaches. One is Kolomogorov test statistic approach and the other two approaches are quantiles of p values and closeness of estimated parameters to the true parameters. These three approaches are discussed below.\\
